Inequalities Witnessing Quantum Incompatibility in The Triangle Scenario

### 2016-09-07 document/main.tex
More work on the extension covering procedure, changed notation again

\usepackage{silence}
\WarningFilter{revtex4-1}{Repair the float}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
% === All of the Packages I use frequently ===
\usepackage{../packages/shared}

@@

% === Commonly re-occurring symbols ===
\newcommand{\hgraph}{\mathcal{H}}
\newcommand{\graph}{\mathcal{G}}
\newcommand{\nodes}{\mathcal{N}}
\newcommand{\weights}{\mathcal{W}}
\newcommand{\edges}{\mathcal{E}}
\newcommand{\trans}{\mathcal{T}}
\newcommand{\ind}{\mathcal{I}}
\newcommand{\perm}{\Omega}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\ancestralindep}{\perp}
\newcommand{\valprod}{\times}
\newcommand{\bigvalprod}{\prod}
\newcommand{\com}{\mathrel{\Yright\hspace{-0.2em}\Yleft}}
\newcommand{\ext}{\mathrel{\Yleft}}
\newcommand{\res}{\mathrel{\Yright}}
\newcommand{\gelem}{\varphi}
\newcommand{\action}[1]{\gelem\bs{#1}}
\newcommand{\mscenario}{\mathcal{M}}
\newcommand{\jointvar}{\mathcal{J}}
\newcommand{\mext}[1]{E_{#1}}
\newcommand{\mul}[1]{\Gamma_{#1}}
\newcommand{\isext}[2]{\delta_{#1 \ext #2}}
\newcommand{\ts}{\mathcal{T}}
% When I introduce a new term or definition
\newcommand{\term}[1]{\textcolor{Mahogany}{\textbf{#1}}}

@@

\setoperator{Pa} % Parents of a node
\setoperator{Ch} % Children of a node
\setoperator{An} % Ancestry of a node
\setoperator{Sub} % subgraph
\setoperator{AnSub} % Ancestral subgraph
\setoperator{Ext} % Extension of outcomes
\setoperator{Com} % Compatible equivalence relation
\setoperator{Nec} % Necessary nodes
\setoperator{UnNec} % Unnecessary nodes
\setoperator{Inj} % injectable sets
\setoperator{ImInj} % images of the injectable sets
\setoperator{PreInj} % Pre-injectable sets
\setoperator{ImPreInj} % images of the Pre-injectable sets
\setoperator{Aut} % graph automorphism
\setoperator{Orb} % Group Orbits
\setoperator{Perm} % Permutation group
\setoperator{Out} % Outcome space
\setoperator{Dom} % Domian

@@

% === To allow for labeling of rows and columns of a matrix ===
\usepackage{kbordermatrix}
\renewcommand{\kbldelim}{(} % Left delimiter
\renewcommand{\kbrdelim}{)} % Right delimiter

@@

\begin{document}
    \title{Inequalities Witnessing Quantum Incompatibility in The Triangle Scenario}
    \author{Thomas C. Fraser}
    \email{tcfraser@tcfraser.com}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada \\ University of Waterloo, Waterloo, Ontario, Canada}
    % \author{Elie Wolfe}
    % \email{ewolfe@perimeter@institute.ca}
    % \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada}
    \date{\today}
    \begin{abstract}
        Causal inference aims to identify which observable distributions are compatible with a given causal structure. Compatibility inequalities for the triangle scenario have been obtained and demonstrated to be violated by quantum configurations. Obtaining these inequalities has lead to the development of new computational techniques suitable for large causal structures with numerous outcomes. Numerical optimizations against these inequalities have found new quantum configurations that are incompatible with the triangle scenario, potentially suggesting new quantum resources qualitatively different from those known previously. \todo[TC]{Write a better abstract.}
    \end{abstract}
    \maketitle
    \tableofcontents

@@

    \begin{definition}
        \label{def:hypergraph}
        A \term{hypergraph} denoted $\hgraph$ is an ordered tuple $\br{\nodes, \edges}$ of \textit{nodes} and \textit{hyperedges} respectively where the nodes can represent any object and the hyperedges are \textit{subsets} of nodes. For convenience of notation, one defines an index set over the nodes and hyperedges of a hypergraph $\hgraph$ denoted $\ind_\nodes$ and $\ind_\edges$ respectively.
        \[ \hgraph = \br{\nodes, \edges} \quad \nodes = \bc{n_i \mid i \in \ind_\nodes} \quad \edges = \bc{e_i \mid i \in \ind_\edges, e_i \subseteq \nodes} \]
        Note that whenever the hyperedge or node index is arbitrary, it will be omitted. There is a dual correspondence between hyperedges $e \in \edges$ and nodes $n \in \nodes$ in a Hypergraph. A hyperedge $e$ is viewed as a set of nodes $\bc{n_i}$, and a node $n$ can be viewed as the set of hyperedges $\bc{e_i}$ that contain it.
    \end{definition}

@@

    \begin{definition}
        The \term{marginalization} of a distribution $\prob[V]$ to a distribution over $W \subseteq V$ is denoted $\sum_{V \setminus W} \prob[V]$ and is defined such that,
        \[ \forall f \in \Out{W} : \br{\sum_{V \setminus W} \prob[V]}\br{f} \defined \sum_{g \in \Ext[V]{f}} \prob[V][g] \]
    \end{definition}

    \subsection{Preliminary Definitions}

    Before discussing the present work, we

    \todo[TC]{How many definitions do I need to write??}

@@

    \begin{definition}
        A \term{causal compatibility inequality} $\mathcal{I}_{\mscenario}$ for a marginal scenario $\mscenario$ is a probabilistic inequality that is obeyed for every compatible marginal model $\prob^{\mscenario}$. Whenever the marginal scenario $\mscenario$ in question is evident by context, the subscript of $\mathcal{I}_{\mscenario}$ will be dropped leaving just $\mathcal{I}$.
    \end{definition}

@@

    As a preliminary search for quantum incompatibility in $\ts$, we performed numerical optimizations using bipartite qubit states and $2$-outcome POVM measurements (see \cref{sec:param_quantum_states} for details) against the $37$ compatibility inequalities printed in \cite{Inflation} as well as the entropic inequalities presented by \cite{Henson_2014}. Unfortunately, none of these inequalities could be violated. These early results suggest, although do not prove, that quantum non-locality is not present in $\ts$ for \textit{two-outcome} measurements. We make \textit{no claim} that this is a universal truth and simply take it as motivation to explore incompatibility in $\ts$ for a larger number of outcomes.

    Specifically, we make use of the inflation technique for an inflated triangle scenario $\ts'$ depicted in \cref{fig:inflated_triangle_scenario} and cast the \textit{causal compatibility} problem as a \textit{marginal problem}. We develop a new technique which we call the \textit{extendable covering procedure (ECP)} to find a complete solution to the marginal problem that is suitable for large causal structures where the observable nodes are equipped with numerous outcomes. We use this technique to find numerous compatibility inequalities, some of which witness the incompatibility of the Fritz distribution. Before discussing the ECP, the Fritz distribution will be re-defined explicitly here, followed by a quick summary of the inflation technique of \cite{Inflation}. Following these summaries of existing work, we present the ECP and its connection to Hardy-type paradoxes \cite{Inflation,Liang_2011,Mansfield_2012}, certificate inequalities and logical Bell inequalities \cite{Abramsky_2011}. Moreover, the ECP can be adapted to derive symmetric inequalities or inequalities bounding any subspace of marginal models. To conclude, we subject our found inequalities to non-linear optimizations and discuss the implications of our results.

@@

    The inflation lemma is the most important result of the causal inflation technique \cite{Inflation}. The contrapositive version of \cref{lem:inflation} is a powerful tool for determining compatibility. Any compatibility constraint on marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ of the inflated causal structure $\graph'$ correspond to valid compatibility constraints on marginal models $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ of the original causal structure. Corollary 5 of \cite{Inflation} proves this explicitly for incompatibility inequalities $\mathcal{I}$; which the remainder of this work focuses on.  Additionally, the inflation lemma holds when considering any subset of $\Inj[\graph]{\graph'}$ (analogously $\ImInj[\graph]{\graph'}$). Therefore, in situations where latent nodes are present in $\graph$, one only needs to consider injectable sets that are composed of \textit{observable nodes}.

@@

    Focusing on the inflation $\ts'$ depicted in \cref{fig:inflated_triangle_scenario}, we obtained the injectable sets $\Inj[\ts]{\ts'}$ along with the maximally pre-injectable sets through a simple graphical procedure outlined in \cite{Inflation}.
    \begin{equation*}
        \eq \label{eq:pre-injectable_triangle_scenario}
        \begin{gathered}
            \textbf{Maximal Pre-injectable Sets} \\
            \bc{A_1, B_1, C_1, A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3, A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1, A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3, A_3, B_1, C_2} \\
            \bc{A_1, B_3, C_4} \\
            \bc{A_1, B_4, C_2} \\
            \bc{A_2, B_1, C_4} \\
            \bc{A_2, B_2, C_2} \\
            \bc{A_3, B_3, C_3} \\
            \bc{A_3, B_4, C_1} \\
            \bc{A_4, B_1, C_3} \\
            \bc{A_4, B_2, C_1}
        \end{gathered}
        \qquad
        \begin{gathered}
            \textbf{Ancestral Independences} \\
            \bc{A_1, B_1, C_1} \ancestralindep \bc{A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3} \ancestralindep \bc{A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1} \ancestralindep \bc{A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3} \ancestralindep \bc{A_3, B_1, C_2} \\
            \bc{A_1} \ancestralindep \bc{B_3} \ancestralindep \bc{C_4} \\
            \bc{A_1} \ancestralindep \bc{B_4} \ancestralindep \bc{C_2} \\
            \bc{A_2} \ancestralindep \bc{B_1} \ancestralindep \bc{C_4} \\
            \bc{A_2} \ancestralindep \bc{B_2} \ancestralindep \bc{C_2} \\
            \bc{A_3} \ancestralindep \bc{B_3} \ancestralindep \bc{C_3} \\
            \bc{A_3} \ancestralindep \bc{B_4} \ancestralindep \bc{C_1} \\
            \bc{A_4} \ancestralindep \bc{B_1} \ancestralindep \bc{C_3} \\
            \bc{A_4} \ancestralindep \bc{B_2} \ancestralindep \bc{C_1}
        \end{gathered}
    \end{equation*}
    As can be counted, there are $12$ maximally pre-injectable sets $\ts'$ which will be indexed $1$ through $12$ in the order seen above ($\bc{V_1, \ldots, V_{12}}$). The maximally pre-injectable sets $\bc{V_i}_{i \in \bs{12}}$ form a maximal marginal scenario $\mscenario$ over the observable nodes of $\ts'$ when equipped with outcome labels. Using \cref{lem:inflation} inequalities $\mathcal{I}_{\PreInj[\ts]{\ts'}}$ constraining the set of contextual marginal models $\prob^{\mscenario}$ can be deflated into polynomial inequalities over $\mathcal{I}_{\ImInj[\ts]{\ts'}}$ bounding compatible marginal models over the images of the injectable sets in $\ts$.
    \[ \ImInj[\ts]{\ts'} = \bc{\bc{A, B, C}, \bc{A}, \bc{B}, \bc{C}} \]

@@

    \[ \mathcal{I}\tsb{Mosek-Cert}, \mathcal{I}\tsb{Cert} \]

@@

    In this section, we will first summarize a method that can be used to obtain a complete solution to the \textit{possibilistic} marginal problem and indirectly offer a \textit{partial} solution to the \textit{probabilistic} marginal problem. Doing so corresponds to enumerating all
    \subsection{Logical Covers}
    In this section, we summarize the familiar notion of a logical cover
    % \begin{lemma}
    %     \label{lemma:logical_extenable_set}
    %     Let $m \in \Out{\mscenario}$ be some marginal outcome of the marginal scenario $\mscenario$. If any marginal model $\prob^{\mscenario}$ is to be non-contextual, the following condition must hold.
    %     \[ m \iff \bigvee_{j \in \Ext[\jointvar]{m}} j \]
    %     The idea being that if a joint distribution exists, then the event $m$ represents partial knowledge of the entire system $\jointvar$; whenever $m$ occurs, exactly one of the extendable joint outcomes has to have occurred.
    % \end{lemma}
    Suppose one has a particular marginal outcome $a \in \Out{\mscenario}$ and a marginal model $\prob^{\mscenario}$ that assigns the probability $\prob[][a]$ to the outcome $a$. If the marginal model $\prob^{\mscenario}$ is to admit a joint distribution $\prob[\jointvar]$, then it must be that $\prob[][a]$ is equal to a marginalization over $a$'s extendable set into $\jointvar$.
    \[ \prob[][a] = \sum_{j \in \Ext[\jointvar]{a}}\prob[\jointvar][j] \eq \label{eq:marginal_extendable_sum_a}\]
    This corresponds to row $a$ of the incidence matrix $M$. Next consider a subset of marginal outcomes $C \subseteq \Out{\mscenario}$. Summing over the associated probabilities $\bc{\prob[][c]}_{c \in C}$ and applying \cref{eq:marginal_extendable_sum_a} yields,
    \[ \sum_{c \in C}\prob[][c] = \sum_{c \in C}\sum_{j \in \Ext[\jointvar]{c}}\prob[\jointvar][j] \eq \label{eq:marginal_extendable_sum_cs} \]
    If for all joint distributions $\prob[\jointvar]$ it can be demonstrated that the following holds,
    \[ \sum_{c \in C}\sum_{j \in \Ext[\jointvar]{c}}\prob[\jointvar][j] \geq \sum_{j \in \Ext[\jointvar]{a}}\prob[\jointvar][j] \eq \label{eq:extendable_cover_first} \]
    Then combining \cref{eq:marginal_extendable_sum_a,eq:marginal_extendable_sum_cs,eq:extendable_cover_first} yields a valid compatibility inequality for $\mscenario$.
    \[ \prob[][a] \leq \sum_{c \in C}\prob[][c] \eq \label{eq:1ncover} \]
    In order for \cref{eq:extendable_cover_first} to hold for \textit{all} joint distributions $\prob[\jointvar]$, it must hold on an algebraic level; each term on the right-hand side of \cref{eq:extendable_cover_first} also appears on the left-hand side of \cref{eq:extendable_cover_first}.\footnote{If there were a joint outcome $j^*$ present on the right-hand side of \cref{eq:extendable_cover_first} but not the left, then \cref{eq:extendable_cover_first} would be violated by the deterministic distribution $\prob[\jointvar][j^*] = 1$} Therefore, identifying all compatibility inequalities that can be written in the form of \cref{eq:1ncover} corresponds to identifying all sets $C \subseteq \Out{\mscenario}$ such that their joint distribution terms algebraically \textit{cover} the joint distribution terms for $a \in \Out{\mscenario}$.

    The notion of forming a

    \subsection{Extendable Covers}
    We will now generalize the notion of a logical cover by considering more exotic antecedents corresponding to multiple marginal outcomes $A \subseteq \Out{\mscenario}$ along with weights $\mul{A}$ for each outcome. Afterwards we demonstrate that these generalized covers also admit non-trivial probabilistic compatibility inequalities.

>>>>

% \usepackage{silence}
% \WarningFilter{revtex4-1}{Repair the float}
% \usepackage{algorithm}
% \usepackage[noend]{algpseudocode}
% === All of the Packages I use frequently ===
\usepackage{../packages/shared}

@@

% === Commonly re-occurring symbols ===
\newcommand{\hgraph}{\mathcal{H}}
\newcommand{\graph}{\mathcal{G}}
\newcommand{\nodes}{\mathcal{N}}
\newcommand{\weights}{\mathcal{W}}
\newcommand{\edges}{\mathcal{E}}
\newcommand{\trans}{\mathcal{T}}
\newcommand{\ind}{\mathcal{I}}
\newcommand{\perm}{\Omega}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\ancestralindep}{\perp}
\newcommand{\valprod}{\times}
\newcommand{\bigvalprod}{\prod}
\newcommand{\com}{\mathrel{\Yright\hspace{-0.2em}\Yleft}}
\newcommand{\ext}{\mathrel{\Yleft}}
\newcommand{\res}{\mathrel{\Yright}}
\newcommand{\gelem}{\varphi}
\newcommand{\action}[1]{\gelem\bs{#1}}
\newcommand{\mscenario}{\mathcal{M}}
\newcommand{\jointvar}{\mathcal{J}}
\newcommand{\mset}[1]{\gamma^{#1}}
\newcommand{\extmset}[1]{\Gamma^{#1}}
\newcommand{\supp}[1]{\si\br{#1}}

% \newcommand{\mext}[1]{E_{#1}}
% \newcommand{\mul}[1]{\Gamma_{#1}}
\newcommand{\isext}[2]{\delta_{#1 \ext #2}}
\newcommand{\ts}{{\graph}}
% When I introduce a new term or definition
\newcommand{\term}[1]{\textcolor{Mahogany}{\textbf{#1}}}

@@

\setoperator{Pa} % Parents of a node
\setoperator{Ch} % Children of a node
\setoperator{An} % Ancestry of a node
\setoperator{Sub} % subgraph
\setoperator{AnSub} % Ancestral subgraph
\setoperator{Ext} % Extension of outcomes
\setoperator{Com} % Compatible equivalence relation
\setoperator{Nec} % Necessary nodes
\setoperator{UnNec} % Unnecessary nodes
\setoperator{Inj} % injectable sets
\setoperator{ImInj} % images of the injectable sets
\setoperator{PreInj} % Pre-injectable sets
\setoperator{ImPreInj} % images of the Pre-injectable sets
\setoperator{Aut} % graph automorphism
\setoperator{Orb} % Group Orbits
\setoperator{Perm} % Permutation group
\setoperator{Out} % Outcome space
\setoperator{Dom} % Domian
% \setoperator{Dom} % Domian
% \setoperator{Dom} % Domian

@@

% === To allow for labeling of rows and columns of a matrix ===
\usepackage{../packages/kbordermatrix}
\renewcommand{\kbldelim}{(} % Left delimiter
\renewcommand{\kbrdelim}{)} % Right delimiter

@@

\begin{document}
    \title{Inequalities Witnessing Quantum Incompatibility in The Triangle Scenario}
    \author{Thomas C. Fraser}
    \email{tcfraser@tcfraser.com}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada \\ University of Waterloo, Waterloo, Ontario, Canada}
    % \author{Elie Wolfe}
    % \email{ewolfe@perimeter@institute.ca}
    % \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada}
    \date{\today}
    \begin{abstract}
        Quantum correlations are often incompatible with a classical assumption of causal structure. This nonclassicality is often known as quantum nonlocality, and it is witnessed through the violation of causal compatability inequalities, such as Bell inequalities. Such inequalities were recently derived for the Triangle scenario [arXiv:1609.00672], begging the question: can these inequalities be violated by quantum correlations? Here we answer this affirmatively, and discuss specific Triangle scenario inequalities and quantum configurations which manifest nonclassical correlations. We also report the development of novel computational techniques suitable for large causal structures with numerous outcomes. Numerical optimzations reveal quantum resources potentially qualitatively different from those known previously.
    \end{abstract}
    \maketitle
    \tableofcontents

@@

@@

    \begin{definition}
        The \term{marginalization} of a distribution $\prob[V]$ to a distribution over $W \subseteq V$ is denoted $\sum_{V \setminus W} \prob[V]$ and is defined such that,
        \[ \forall f \in \Out{W} : \br{\sum_{V \setminus W} \prob[V]}\br{f} \defined \sum_{g \in \Ext[V]{f}} \prob[V][g] \]
    \end{definition}
    \comment[TC]{How many definitions do I need to write??}

@@

    \begin{definition}
        A \term{causal compatibility inequality} $I_{\mscenario}$ for a marginal scenario $\mscenario$ is a probabilistic inequality that is obeyed for every compatible marginal model $\prob^{\mscenario}$. Whenever the marginal scenario $\mscenario$ in question is evident by context, the subscript of $I_{\mscenario}$ will be dropped leaving just $I$.
    \end{definition}

@@

    As a preliminary search for quantum incompatibility in $\ts$, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements (see \cref{sec:param_quantum_states} for details) against the $37$ compatibility inequalities printed in \cite{Inflation} as well as the entropic inequalities presented by \cite{Henson_2014}. Unfortunately, none of these inequalities could be violated. These early results suggest, although do not prove, that quantum non-locality is not present in $\ts$ for \textit{two-outcome} measurements. We make \textit{no claim} that this is a universal truth and simply take it as motivation to explore incompatibility in $\ts$ for a larger number of outcomes.

    Specifically, we make use of the inflation technique for an inflated triangle scenario $\ts'$ depicted in \cref{fig:inflated_triangle_scenario} and cast the \textit{causal compatibility} problem as a \textit{marginal problem}. We develop a new technique which we call the \textit{extension covering procedure (ECP)} to find a complete solution to the marginal problem that is suitable for large causal structures where the observable nodes are equipped with numerous outcomes. We use this technique to find numerous compatibility inequalities, some of which witness the incompatibility of the Fritz distribution. Before discussing the ECP, the Fritz distribution will be re-defined explicitly here, followed by a quick summary of the inflation technique of \cite{Inflation}. Following these summaries of existing work, we present the ECP and its connection to Hardy-type paradoxes \cite{Inflation,Liang_2011,Mansfield_2012}, certificate inequalities and logical Bell inequalities \cite{Abramsky_2011}. Moreover, the ECP can be adapted to derive symmetric inequalities or inequalities bounding any subspace of marginal models. To conclude, we subject our found inequalities to non-linear optimizations and discuss the implications of our results.

@@

    The inflation lemma is the most important result of the causal inflation technique \cite{Inflation}. The contrapositive version of \cref{lem:inflation} is a powerful tool for determining compatibility. Any compatibility constraint on marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ of the inflated causal structure $\graph'$ correspond to valid compatibility constraints on marginal models $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ of the original causal structure. Corollary 5 of \cite{Inflation} proves this explicitly for incompatibility inequalities $I$; which the remainder of this work focuses on.  Additionally, the inflation lemma holds when considering any subset of $\Inj[\graph]{\graph'}$ (analogously $\ImInj[\graph]{\graph'}$). Therefore, in situations where latent nodes are present in $\graph$, one only needs to consider injectable sets that are composed of \textit{observable nodes}.

@@

    Focusing on the inflation $\ts'$ depicted in \cref{fig:inflated_triangle_scenario}, we obtained the injectable sets $\Inj[\ts]{\ts'}$ along with the maximally pre-injectable sets through a simple graphical procedure outlined in \cite{Inflation}.
    \begin{equation*}
        \eq \label{eq:pre-injectable_triangle_scenario}
        \begin{gathered}
            \textbf{Maximal Pre-injectable Sets} \\
            \bc{A_1, B_1, C_1, A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3, A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1, A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3, A_3, B_1, C_2} \\
            \bc{A_1, B_3, C_4} \\
            \bc{A_1, B_4, C_2} \\
            \bc{A_2, B_1, C_4} \\
            \bc{A_2, B_2, C_2} \\
            \bc{A_3, B_3, C_3} \\
            \bc{A_3, B_4, C_1} \\
            \bc{A_4, B_1, C_3} \\
            \bc{A_4, B_2, C_1}
        \end{gathered}
        \qquad
        \begin{gathered}
            \textbf{Ancestral Independences} \\
            \bc{A_1, B_1, C_1} \ancestralindep \bc{A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3} \ancestralindep \bc{A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1} \ancestralindep \bc{A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3} \ancestralindep \bc{A_3, B_1, C_2} \\
            \bc{A_1} \ancestralindep \bc{B_3} \ancestralindep \bc{C_4} \\
            \bc{A_1} \ancestralindep \bc{B_4} \ancestralindep \bc{C_2} \\
            \bc{A_2} \ancestralindep \bc{B_1} \ancestralindep \bc{C_4} \\
            \bc{A_2} \ancestralindep \bc{B_2} \ancestralindep \bc{C_2} \\
            \bc{A_3} \ancestralindep \bc{B_3} \ancestralindep \bc{C_3} \\
            \bc{A_3} \ancestralindep \bc{B_4} \ancestralindep \bc{C_1} \\
            \bc{A_4} \ancestralindep \bc{B_1} \ancestralindep \bc{C_3} \\
            \bc{A_4} \ancestralindep \bc{B_2} \ancestralindep \bc{C_1}
        \end{gathered}
    \end{equation*}
    As can be counted, there are $12$ maximally pre-injectable sets $\ts'$ which will be indexed $1$ through $12$ in the order seen above ($\bc{V_1, \ldots, V_{12}}$). The maximally pre-injectable sets $\bc{V_i}_{i \in \bs{12}}$ form a maximal marginal scenario $\mscenario$ over the observable nodes of $\ts'$ when equipped with outcome labels. Using \cref{lem:inflation} inequalities $I_{\PreInj[\ts]{\ts'}}$ constraining the set of contextual marginal models $\prob^{\mscenario}$ can be deflated into polynomial inequalities over $I_{\ImInj[\ts]{\ts'}}$ bounding compatible marginal models over the images of the injectable sets in $\ts$.
    \[ \ImInj[\ts]{\ts'} = \bc{\bc{A, B, C}, \bc{A}, \bc{B}, \bc{C}} \]
    \comment[TC]{This is not all the images. I should clarify this.}

@@

    \[ I\tsb{Mosek-Cert}, I\tsb{Cert} \]

@@

    In this section, we will first summarize a method that can be used to obtain a complete solution to the \textit{possibilistic} marginal problem and indirectly offer a \textit{partial} solution to the \textit{probabilistic} marginal problem. Doing so corresponds to enumerating all
    \subsection{Logical Covers}
    In this section, we summarize the familiar notion of logical implications as witnesses for contextuality. Let $a \in \Out{\mscenario}$ be a marginal outcome and let $C = \bc{c_1, \ldots, c_{\abs{C}}} \subseteq \Out{\mscenario}$ be a subset of marginal outcomes. The subset $C$ is a \term{logical cover} of $a$ if the following possibilistic statement holds for \textit{all} marginal models $\prob^{\mscenario}$.
    \[ a \implies c_1 \vee \ldots \vee c_{\abs{C}} = \bigvee_{c \in C} c \eq \label{eq:1a_implication} \]
    The marginal outcome $a$ will be referred to as the \textit{antecedent} and $C$ as the \textit{consequent set}. A marginal model $\prob^{\mscenario}$ satisfies \cref{eq:1a_implication} if there always exists at least one $c \in C$ that is possible ($\prob[][c] > 0$) whenever $a$ is possible. A marginal model $\prob^{\mscenario}$ violates \cref{eq:1a_implication} whenever \textit{none} of the outcomes in $C$ are possible while $a$ is nonetheless still possible. Marginal models that violate logical statements such as \cref{eq:1a_implication} are known as \term{Hardy Paradoxes} \cite{Inflation,Mansfield_2012,Mancinska_2014}. The concept of witnessing quantum incompatibility on a logical level has been analyzed thoroughly for decades \cite{Greenberger_1990,Abramsky_2012}; being motivated by a false sense of robustness compared to probabilistic constraints. Logical covers such as \cref{eq:1a_implication} are in one-to-one correspondence with a subset of probabilistic inequalties.

    \begin{lemma}
        \label{lemma:logical_extenable_set}
        Let $a \in \Out{\mscenario}$ be some marginal outcome of the marginal scenario $\mscenario$. If any marginal model $\prob^{\mscenario}$ is to be non-contextual, the following condition must hold.
        \[ a \iff \bigvee_{j \in \Ext[\jointvar]{a}} j \eq \label{eq:lemma_logical_extendable_set}\]
    \end{lemma}
    The idea being that if a joint distribution exists, then the event $a$ represents partial knowledge of the entire system $\jointvar$; whenever $a$ occurs, exactly one of the extendable joint outcomes has to have occurred. Likewise \cref{lemma:logical_extenable_set} applies to a collection of marginal outcomes $C \in \Out{\mscenario}$,
    \[ \bigvee_{c \in C} c \iff \bigvee_{c \in C} \bigvee_{j \in \Ext[\jointvar]{c}} j \eq \label{eq:logical_extension_C}\]
    If a subset $C$ can be constructed such that its extension \textit{covers} the extendable set of $a$,
    \[ \Ext[\jointvar]{a} \subseteq \bigcup_{c \in C} \Ext[\jointvar]{c} \eq \label{eq:logical_containment} \]
    Then the combination of \cref{eq:lemma_logical_extendable_set,eq:logical_extension_C,eq:logical_containment} yields \cref{eq:1a_implication}. Hence the motivation for calling \cref{eq:1a_implication} a logical cover.

    The principle statement of \cref{lemma:logical_extenable_set} can be taken in a probabilistic form. If the marginal model $\prob^{\mscenario}$ is to admit a joint distribution $\prob[\jointvar]$, then it must be that the probability $\prob[][a]$ of any marginal outcome $a \in \Out{\mscenario}$ is equal to a marginalization over its extendable set into $\jointvar$.
    \[ \prob[][a] = \sum_{j \in \Ext[\jointvar]{a}}\prob[\jointvar][j] \eq \label{eq:marginal_extendable_sum_a} \]
    A logical cover $C \subseteq \Out{\mscenario}$ of $a$ has probabilistic extension,
    \[ \sum_{c \in C}\prob[][c] = \sum_{c \in C}\sum_{j \in \Ext[\jointvar]{c}}\prob[\jointvar][j] \eq \label{eq:marginal_extendable_sum_cs} \]
    Since $C$ is a logical cover of $a$, the right-hand side of \cref{eq:marginal_extendable_sum_a} algebraically covers \cref{eq:marginal_extendable_sum_cs}\footnote{If there were a joint outcome $j^*$ present on the right-hand side of \cref{eq:marginal_extendable_sum_a} but not the right-hand side of \cref{eq:marginal_extendable_sum_cs}, then \cref{eq:1a_probabilistic} would be violated by the deterministic distribution $\prob[\jointvar][j^*] = 1$}. Therefore one recovers a probabilistic version of \cref{eq:1a_implication},
    \[ \prob[][a] \leq \sum_{c \in C}\prob[][c] \eq \label{eq:1a_probabilistic} \]
    \begin{remark}
        It is also possible to recover \cref{eq:1a_probabilistic} from \cref{eq:1a_implication} directly, by putting \cref{eq:1a_implication} into disjunction normal form and assigning it a certain probability,
        \[ \prob[][\neg a \vee \bigvee_{c \in C} c] = 1 \]
        Then applying Boole's indentity and the negative rule $\prob[][\neg a] = 1 - \prob[][a]$ one recovers \cref{eq:1a_probabilistic}.
    \end{remark}
    \begin{remark}
        The probabilistic logical cover \cref{eq:1a_probabilistic} is an \textit{upgraded} version of \cref{eq:1a_implication} in the following sense.
        \begin{itemize}
            \item Every non-contextual marginal model $\prob^{\mscenario}$ satisfies both \cref{eq:1a_probabilistic} and \cref{eq:1a_implication}.
            \item Every contextual marginal model $\prob^{\mscenario}$ that violates \cref{eq:1a_implication} will also violate \cref{eq:1a_probabilistic}; but the converse is not necessarily true.
        \end{itemize}
    \end{remark}

    Computationally enumerating all logical covers for a particular antecedent $a$ corresponds to a hypergraph transversal problem \cite{Inflation}, an idea we return to in the more general picture to follow.

    \subsection{Extension Covers}
    We will now generalize the notion of a logical cover by considering more exotic antecedents corresponding to multiple marginal outcomes along with weights $\mset{A}$ for each outcome. Afterwards we demonstrate that these generalized covers also admit non-trivial probabilistic compatibility inequalities.

    \begin{definition}
        We first define the marginal indicator vector $\de_{m}$ to be the unit vector indexed by marginal outcomes $\Out{\mscenario}$ that is $1$ whenever the index is $m$, and $0$ otherwise.
        \[ \de_{m}\br{m} = 1 \quad \forall m' \neq m : \de_{m} \br{m'} = 0 \]
        Analogously defined is the joint indicator vector $\de_{j}$.
        \[ \de_{j}\br{j} = 1 \quad \forall j' \neq j : \de_{j} \br{j'} = 0 \]
    \end{definition}

    We first recall that every non-contextual marginal model $\prob^{\mscenario}$ can be written as the convex combination of columns of the incidence matrix $M$.
    \[ \probvec^{\mscenario} = M \cdot \probvec[\jointvar] = \sum_{j \in \Out{\jointvar}} \de_{m \ext j} \prob[\jointvar][j] \]
    Thus we define the set of all non-contextual marginal models as $\mathcal{NC}$,
    \[ \mathcal{NC} \defined \bc{\probvec^{\mscenario} \mid \probvec^{\mscenario} = \sum_{j} \mu_{j} \de_{j \res \mscenario}, \mu_j \geq 0, \sum_{j} \mu_{j} = 1} \]

    \begin{definition}
        Let $\mscenario$ be a marginal scenario and let $m \in \Out{\mscenario}$ be a marginal outcome. The \term{extension of $m$ onto $\jointvar$} is the function $\de_{m \ext \jointvar} : \Out{\jointvar} \to \bc{0, 1}$ that indicates membership of $\Ext[\jointvar]{m}$.
        \[ \de_{m \ext \jointvar}\br{j} \defined \begin{cases}
            1 & j \ext m \\
            0 & \textrm{otherwise}
        \end{cases} \]
        As a vector indexed by joint outcomes $j \in \Out{\jointvar}$, $\de_{m \ext \jointvar}$ is precisely the $m$-th row of the incidence matrix.
    \end{definition}
    \begin{definition}
        Let $\mscenario$ be a marginal scenario and let $j \in \Out{\jointvar}$ be a joint outcome. The \term{restriction of $j$ onto $\mscenario$} is deterministic marginal model $\de_{j \res \mscenario} : \Out{\mscenario} \to \bc{0, 1}$.
        \[ \de_{j \res \mscenario}\br{m} \defined \begin{cases}
            1 & j \ext m  \\
            0 & \textrm{otherwise}
        \end{cases} \]
        As a vector indexed by marginal outcomes $m \in \Out{\mscenario}$, $\de_{j \ext \mscenario}$ is precisely the $j$-th column of the incidence matrix.
    \end{definition}

    \begin{definition}
        A \term{multiplicity set} or \term{m-set} $\mset{S}$ for a marginal scenario $\mscenario$ is a vector indexed by marginal outcomes $m \in \Out{\mscenario}$ whose entries are non-negative integers $\mset{S}_{m} \in \Z_{\geq 0}$. The \term{support} $\supp{\mset{S}}$ of an m-set is the set of marginal outcomes that are assigned strictly positive multiplicity.
        \[ \supp{\mset{S}} \defined \bc{m \in \Out{\mscenario} \mid \mset{S}_m \in \N} \]
    \end{definition}
